An indexed construction of semi-simplicial and semi-cubical types

### 2022-05-20 paper/paper.tex
paper: reorder tables; tab:coind first

\section{Trunacated \texorpdfstring{$n$}{n}-sets}
In this section, we give the core of the definition of truncated $n$-sets
as a coinductive limit.

@@

\input{tab-core.tex}
\input{tab-frames.tex}
\input{tab-faces.tex}
\input{tab-coh.tex}
\input{tab-coind.tex}

>>>>

\section{Reasoning on \texorpdfstring{$\nu$}{nu}-sets}
In this section, we give the core of the definition of truncated $\nu$-sets
as a coinductive limit.

@@

\input{tab-coind.tex}
\input{tab-core.tex}
\input{tab-frames.tex}
\input{tab-faces.tex}
\input{tab-coh.tex}
